Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Quasiperiodic Variables from TESS

### 2023-08-13 paper/ms.tex
re-classify three CQVs
dropped entirely:
  TIC 251496897 (alpha per / s58)
  TIC 302160226 (s58)

good->maybe:
  TIC 5714469

Of the \ngoodsfieldbanyan\ stars for which BANYAN\,$\Sigma$ did not
find any association, one (TIC~302160226) is a member of $\alpha$~Per
($t\approx 86\pm16$\,Myr;
\citealt{2021A&A...645A..84M,2023AJ....166...14B}).  For the other two
(TIC~58084670 and TIC~141146667), we were not able to confidently
associate either star with any young groups.  Both do seem to
show the CQV signal over multiple TESS sectors, and both are
photometrically elevated relative to the main sequence.  
Both were also noted by \citet{2021ApJ...917...23K} as being in the
``diffuse'' population of $<$50\,Myr stars near the Sun.

@@

\startlongtable
\begin{deluxetable}{rrrrrrlrllrrrr}
\tabletypesize{\footnotesize}
%\tabletypesize{\scriptsize}
\tablecaption{Bonafide, candidate, and debunked complex quasiperiodic
  variables from the TESS 2-minute data. {\bf For internal
  review, full versions are available here
  \url{https://www.dropbox.com/scl/fo/twn4s9ckbevf75jqhtoy1/h?rlkey=t5cn8cx2uoc2ptdm9e570kp1b&dl=0}} \label{tab:thetable}}
%\toprule
%TIC & $T$ & $d$ & BP-RP & RUWE & $P$ & assoc & age & teff & rstar & mstar & rcr & qual & Nsectors \\
%\midrule
%\endhead
\startdata
TIC & $T$ & $d$ & $\bprp$ & RUWE & $P$ & Assoc & Age & $T_{\rm eff}$ & $R_\star$ & $M_\star$ & $R$$_{\rm cr}$ & Quality & $N_{\rm sector}$ \\
-- & mag & pc & mag & -- & hr & -- & Myr & K & $R_\odot$ & $M_\odot$ & $R_\star$ & -- & -- \\
\hline
\input{20230613_LGB_RJ_CPV_TABLE_selfnapplied_rounded_data}
\enddata
\tablecomments{This table includes \ngoods\ CQVs (\texttt{Quality}
  flag 1), \nmaybes\ ambiguous CQVs (\texttt{Quality} flag 0), and
  \ndebunked\ impostors (\texttt{Quality} flag -1).  The
  machine-readable version, available online, includes additional
  columns for the Gaia DR2 source identifiers and parameter
  uncertainties.  The age uncertainties are typically $\approx \pm
  10\%$, but can be asymmetric.  {\bf The median temperature, radius, and
  mass uncertainties are $\pm XXX$\,K, $\pm XX$\%, and $\pm YY$\%
  respectively}.  $N_{\rm sector}$ denotes the number of TESS sectors
  for which data are expected to be acquired between July~2018 and
  Oct~2024.   Association names and provenance follow conventions
  adopted by \citet{2018ApJ...856...23G}: 
	ABDMG: AB~Doradus moving group \citep{2015MNRAS.454..593B}.
	ARG: Argus \citep{2019ApJ...870...27Z}.
	APER: $\alpha$~Persei open cluster \citep{2023AJ....166...14B}.
	BPMG: $\beta$~Pic moving group \citep{2015MNRAS.454..593B}.
  CARN: Carina Near moving group \citep{2006ApJ...649L.115Z}.
	COL: Columba \citep{2015MNRAS.454..593B}.
	EPSC: $\epsilon$ Chamaeleontis \citep{2013MNRAS.435.1325M}.
	LCC: Lower Centaurus Crux \citep{2016MNRAS.461..794P}.
	PERI: Pisces-Eridani \citep{2019AJ....158...77C}.
	PLE: Pleiades \citep{2015ApJ...813..108D}.
	TAU: Taurus \citep{1995ApJS..101..117K}.
	THA: Tucana-Horologium assocation \citep{2015MNRAS.454..593B}.
	TWA: TW Hydrae assocation \citep{2015MNRAS.454..593B}.
	UCL: Upper Centaurus Lupus \citep{2016MNRAS.461..794P}.
	USCO: Upper Scorpius \citep{2016MNRAS.461..794P}.
}
\end{deluxetable}
\clearpage

>>>>

For the \ngoodsfieldbanyan\ stars for which BANYAN\,$\Sigma$ did not
find any association, we were not able to confidently associate either
star with any young groups.  Both do seem to show the CQV signal over
multiple TESS sectors, and both are photometrically elevated relative
to the main sequence.  Both were also noted by
\citet{2021ApJ...917...23K} as being in the ``diffuse'' population of
$<$50\,Myr stars near the Sun.

@@

\startlongtable
\begin{deluxetable}{rrrrrrlrllrrrr}
\tabletypesize{\footnotesize}
%\tabletypesize{\scriptsize}
\tablecaption{Bonafide, candidate, and debunked complex quasiperiodic
  variables from the TESS 2-minute data. {\bf For internal
  review, full versions are available here
  \url{https://www.dropbox.com/scl/fo/twn4s9ckbevf75jqhtoy1/h?rlkey=t5cn8cx2uoc2ptdm9e570kp1b&dl=0}} \label{tab:thetable}}
%\toprule
%TIC & $T$ & $d$ & BP-RP & RUWE & $P$ & assoc & age & teff & rstar & mstar & rcr & qual & Nsectors \\
%\midrule
%\endhead
\startdata
TIC & $T$ & $d$ & $\bprp$ & RUWE & $P$ & Assoc & Age & $T_{\rm eff}$ & $R_\star$ & $M_\star$ & $R$$_{\rm cr}$ & Quality & $N_{\rm sector}$ \\
-- & mag & pc & mag & -- & hr & -- & Myr & K & $R_\odot$ & $M_\odot$ & $R_\star$ & -- & -- \\
\hline
\input{20230613_LGB_RJ_CPV_TABLE_selfnapplied_rounded_data}
\enddata
\tablecomments{This table includes \ngoods\ CQVs (\texttt{Quality}
  flag 1), \nmaybes\ ambiguous CQVs (\texttt{Quality} flag 0), and
  \ndebunked\ impostors (\texttt{Quality} flag -1).  The
  machine-readable version, available online, includes additional
  columns for the Gaia DR2 source identifiers and parameter
  uncertainties.  The age uncertainties are typically $\approx \pm
  10\%$, but can be asymmetric.  {\bf The median temperature, radius, and
  mass uncertainties are $\pm XXX$\,K, $\pm XX$\%, and $\pm YY$\%
  respectively}.  $N_{\rm sector}$ denotes the number of TESS sectors
  for which data are expected to be acquired between July~2018 and
  Oct~2024.   Association names and provenance follow conventions
  adopted by \citet{2018ApJ...856...23G}: 
	ABDMG: AB~Doradus moving group \citep{2015MNRAS.454..593B}.
	ARG: Argus \citep{2019ApJ...870...27Z}.
	%APER: $\alpha$~Persei open cluster \citep{2023AJ....166...14B}.
	BPMG: $\beta$~Pic moving group \citep{2015MNRAS.454..593B}.
  CARN: Carina Near moving group \citep{2006ApJ...649L.115Z}.
	COL: Columba \citep{2015MNRAS.454..593B}.
	EPSC: $\epsilon$ Chamaeleontis \citep{2013MNRAS.435.1325M}.
	LCC: Lower Centaurus Crux \citep{2016MNRAS.461..794P}.
	PERI: Pisces-Eridani \citep{2019AJ....158...77C}.
	PLE: Pleiades \citep{2015ApJ...813..108D}.
	TAU: Taurus \citep{1995ApJS..101..117K}.
	THA: Tucana-Horologium assocation \citep{2015MNRAS.454..593B}.
	TWA: TW Hydrae assocation \citep{2015MNRAS.454..593B}.
	UCL: Upper Centaurus Lupus \citep{2016MNRAS.461..794P}.
	USCO: Upper Scorpius \citep{2016MNRAS.461..794P}.
}
\end{deluxetable}
\clearpage
